Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-05-05 research_proposal/research_proposal_draft.qmd
Added grouped fig, and small fix

The hierarchical structure can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the individual series. When there are attributes of interest that are crossed, such as the electricity demand of any aggregation level (national, state, or regional) can be further broken down by usage purposes (e.g., residential, commercial), it will become a grouped time series.

![Diagram of 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png){#fig-hierarchy width="40%"}

@@

The proposed MinT approach by @Wickramasuriya2019-xq uses the shrinkage estimator from @Schafer2005-yw. \textcolor{red}{It guarantees positive definiteness and huge variance reduction when $p>T$}. The shrinkage estimator is given by:

>>>>

The hierarchical structure can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the individual series. When there are attributes of interest that are crossed, such as the electricity demand of any aggregation level (national, state, or regional) can be further broken down by usage purposes (e.g., residential, commercial), it will become a grouped time series (illustrated in @fig-grouped).

![Diagram of 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png){#fig-hierarchy width="40%" height="40%"}

![Diagram of 2-level grouped structure, and can be considered as the union of two hierarchical trees with common top and bottom level series](D:/Github/Recon_Honours_Thesis/research_proposal/figs/grouped_structure.png){#fig-grouped width="90%" height="40%"}

@@

The proposed MinT approach by @Wickramasuriya2019-xq uses the shrinkage estimator from @Schafer2005-yw. \textcolor{red}{It guarantees positive definiteness and variance reduction for the covariance matrix, especially when $p>T$}. The shrinkage estimator is given by:
